---
title: "Quality Control"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.show = 'hold')
```

### Source functions
```{r}
source("QC_functions.R")
```


### NA values

One thing to look at is how many features showed up as NA across each subject by noise processing method.

```{r}
theme_set(cowplot::theme_cowplot())
data_path <- "D:/Virtual_Machines/Shared_Folder/PhD_work/data/scz/UCLA/"
rdata_path <- paste0(data_path, "Rdata/")

NA_subjects_data <- find_catch22_na(rdata_path = rdata_path)
NA_subjects_data
```

This shows that there are six subjects for whom catch22 returned NA values for all ROIs (82) and 19 out of the 22 features for a total of 1,558 NAs per subject. We can load in the raw time-series datasets and view the raw values for these subjects.

```{r}
plot_catch22_na_ts(rdata_path=rdata_path, 
                   subject_IDs=NA_subjects_data$Subject_ID)
```
```{r, echo=F, eval=F}
ggsave("plots/Raw_fMRI_Signal_NA_Subjects.png",
       width=7, height=6, units="in", dpi=300)
```


### Movement -- fractional displacement

We can compile the subjects' average fractional displacement (FD) in the scanner into a dataframe:
```{r}
movement_data <- compile_movement_data(fd_path=paste0(data_path, "movementData/"),
                                       subject_csv = paste0(data_path, "participants.csv"))

head(movement_data)
```
Visualize the average FD by diagnosis in a boxplot:
```{r}
plot_FD_vs_diagnosis(movement_data = movement_data)
```
```{r, echo=F, eval=F}
ggsave("plots/Subject_FD_by_Diagnosis.png",
       width=4, height=4, units="in", dpi=300)
```

Plot the number of subjects retained at each FD threshold:
```{r}
plot_subjects_per_fd_threshold(movement_data)
```
```{r, echo=F, eval=F}
ggsave("plots/Subjects_Retained_by_FD_Threshold.png",
       width=5, height=4, units="in", dpi=300)
```

```{r}
fd_thresh_list <- list()
for (fd_threshold in seq(0, 1, by=0.01)) {
  num_ctrl = nrow(subset(movement_data, FD <= fd_threshold & diagnosis=="CONTROL"))
  num_schz = nrow(subset(movement_data, FD <= fd_threshold & diagnosis=="SCHZ"))
  thresh_df <- data.frame(FD_Threshold = fd_threshold,
                          Control = num_ctrl,
                          Schizophrenia = num_schz)
  fd_thresh_list <- rlist::list.append(fd_thresh_list, thresh_df)
}
threshold_data <- do.call(plyr::rbind.fill, fd_thresh_list) %>%
  mutate(SCZ_to_CTRL = Schizophrenia / Control)

threshold_data %>%
  ggplot(data=., mapping=aes(x=FD_Threshold, y=SCZ_to_CTRL)) +
  geom_line(size=2) +
  ylab("SCZ:CTRL Ratoi") +
  xlab("FD Threshold") +
  scale_x_reverse() +
  ggtitle("Ratio of SCZ:CTRL Subjects Retained\nby FD Threshold") +
  theme(legend.position="bottom",
        plot.title=element_text(hjust=0.5))

ggsave("plots/SCZ_to_CTRL_Retained_by_FD_Threshold.png",
       width=5, height=4, units="in", dpi=300)
```

